---
title: "6371 Project Data Cleaning 1"
author: "Jonathan Tan"
date: "7/31/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
GOALS
1 - Estimate how SalePrice of house is related to GrLIvArea (square footage) in NAmes, Edwards, and BrkSide neighborhoods
  - Find if SalesPrices and relationship to GrLIvArea changes depending on the neighborhood
  - Estimates with confidence intervals, evidence of model assumptions (being met), identify outliers
  - Provide conclusion that states the relationship between Area and SalesPrice for each neighborhood (3) 

2 - Build predictive model for sales prices of all homes in Ames Iowa
  - 4 model types: forward selection, backwards elimination, stepwise selection, one custom
  - Generate adjusted R62, CV Press, and Kaggle Score for each model and format in table
  - conclude which model has the best results in predicting sale prices
```{r data import1}
train.data1 <- read.csv("D:/SMU/DS 6371 Stat Foundations For Data Science/PROJECT/train.csv")
test.data1 <- read.csv("D:/SMU/DS 6371 Stat Foundations For Data Science/PROJECT/test.csv")
```

```{r check for NA's in relevent fields}
#sum(is.na(train.data1$Id))
#sum(is.na(train.data1$SalePrice))
#sum(is.na(train.data1$GrLivArea))
#sum(is.na(train.data1$Neighborhood))

#sum(is.na(test.data1$Id))
#sum(is.na(test.data1$SalePrice))
#sum(is.na(test.data1$GrLivArea))
#sum(is.na(test.data1$Neighborhood))

#so looks all clear, no NA's in either sets' ID, neighborhood, area, or sale price fields
```

```{r distribution sketch}
library(tidyverse)
sample1 <- data.frame(train.data1$Id, train.data1$Neighborhood, train.data1$GrLivArea, train.data1$SalePrice)

names(sample1) <- c("ID", "Neighborhood", "Area", "SalePrice")

sample2 <- sample1[which( sample1$Neighborhood == "NAmes" | sample1$Neighborhood == "Edwards" | sample1$Neighborhood == "BrkSide" ), ] #filter by neighborhoods

#summary of all data
a <- merge(x = test.data1, y = train.data1, by = c("Id", "Neighborhood", "GrLivArea"), all = TRUE)
a1 <- data.frame(a$Id, a$Neighborhood, a$GrLivArea)
names(a1) <- c("Id", "Neighborhood", "Area")
a2 <- a1[which(a1$Neighborhood == "NAmes" | a1$Neighborhood == "Edwards" | a1$Neighborhood == "BrkSide"), ]
```
Assumptions of linear regression 
- Linearity (linearity relationship between independent and dependent variables  (normally distributed on line))
- Normality - multivariate normality (means on the line)
- Equal Standard Deviations - same subpopulation standard deviations(equal spread)
- Independent (subpopulation observations are independent of any other subpopulation observation)
kinda have to assume this one, otherwise the data is unusable?? 

```{r check linearity q1}
#sample 1 is the training dataset, down to relevant 4 columns for q1
plot(sample1$Area, sample1$SalePrice)
#looks mostly linear
plot(sample1$Area, log(sample1$SalePrice))
#log sale price looks a little better
plot(log(sample1$Area), log(sample1$SalePrice))
#ehhhh
plot(sqrt(sample1$Area), sample1$SalePrice)
#practically no change from original run
plot(sample1$Area, sqrt(sample1$SalePrice))
#also dubious
#come back to this later 
```

```{r test multivariate normality }
#???
```

```{r test equal standard deviations}



#plot stuff
plot(sample2$Area, sample2$Neighborhood, ylab = "BrkSide           Edwards           NAmes", main = "Training Data Area by Neighborhood")
plot(a2$Area, a2$Neighborhood, ylab = "BrkSide           Edwards           NAmes", main = "All Data Area By Neighborhood")
#looks skewed, with some extreme outliers for area and price on Edwards and 
```
```{r cleaning more data}
x <- colSums(is.na(train.data1)) #list of na's per column
y <- as.data.frame(x)
z <- subset(y, x != 0) #show only fields that have NA's in them 
names(z) <- c( "Number of NA's")
z

```
We can see that the following columns/data fields are incomplete, with the number of NA's in the right column 
the total observations of the training dataset is 1460, so some of these variables are worth much less than others. 
For example 1369/1460 houses have no data on "Alley", so that's probably not a good variable to base the problem 2 model on. 

```{r model building}
#separate the data into 3 neighborhoods, and do separate models for each, single linear regression style
train.NAmes <- sample1[which( sample1$Neighborhood == "NAmes" ), ]
train.Edwards <- sample1[which( sample1$Neighborhood == "Edwards" ), ]
train.BrkSide <- sample1[which( sample1$Neighborhood == "BrkSide" ), ]

model.NAmes <- lm(formula = SalePrice ~ Area, data = train.NAmes)
model.Edwards <- lm(formula = SalePrice ~ Area, data = train.Edwards)
model.BrkSide <- lm(formula = SalePrice ~ Area, data = train.BrkSide)

#compare to whole model with neighborhood as additional variable

train.hoods <- lm(formula = SalePrice ~ Area + Neighborhood, data = sample2)

summary(train.hoods)

confint(train.hoods)
#questionable results, will come back to this later 
```
