---
title: "6371 Project Data Cleaning 1"
author: "Jonathan Tan"
date: "7/31/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
GOALS
1 - Estimate how SalePrice of house is related to GrLIvArea (square footage) in NAmes, Edwards, and BrkSide neighborhoods
  - Find if SalesPrices and relationship to GrLIvArea changes depending on the neighborhood
  - Estimates with confidence intervals, evidence of model assumptions (being met), identify outliers
  - Provide conclusion that states the relationship between Area and SalesPrice for each neighborhood (3) 

2 - Build predictive model for sales prices of all homes in Ames Iowa
  - 4 model types: forward selection, backwards elimination, stepwise selection, one custom
  - Generate adjusted R62, CV Press, and Kaggle Score for each model and format in table
  - conclude which model has the best results in predicting sale prices
```{r data import1}
train.data1 <- read.csv("D:/SMU/DS 6371 Stat Foundations For Data Science/PROJECT/train.csv")
test.data1 <- read.csv("D:/SMU/DS 6371 Stat Foundations For Data Science/PROJECT/test.csv")
```

```{r check for NA's in relevent fields}
sum(is.na(train.data1$Id))
sum(is.na(train.data1$SalePrice))
sum(is.na(train.data1$GrLivArea))
sum(is.na(train.data1$Neighborhood))

sum(is.na(test.data1$Id))
sum(is.na(test.data1$SalePrice))
sum(is.na(test.data1$GrLivArea))
sum(is.na(test.data1$Neighborhood))

#so looks all clear, no NA's in either sets' ID, neighborhood, area, or sale price fields
```

```{r distribution sketch}
library(tidyverse)
sample1 <- data.frame(train.data1$Id, train.data1$Neighborhood, train.data1$GrLivArea, train.data1$SalePrice)

names(sample1) <- c("ID", "Neighborhood", "Area", "SalePrice")

sample2 <- sample1[which( sample1$Neighborhood == "NAmes" | sample1$Neighborhood == "Edwards" | sample1$Neighborhood == "BrkSide" ), ] #filter by neighborhoods

#summary of all data
a <- merge(x = test.data1, y = train.data1, by = c("Id", "Neighborhood", "GrLivArea"), all = TRUE)
a1 <- data.frame(a$Id, a$Neighborhood, a$GrLivArea)
names(a1) <- c("Id", "Neighborhood", "Area")
a2 <- a1[which(a1$Neighborhood == "NAmes" | a1$Neighborhood == "Edwards" | a1$Neighborhood == "BrkSide"), ]
```


```{r initvis}
#plot stuff
plot(sample2$Area, sample2$Neighborhood, ylab = "BrkSide           Edwards           NAmes", main = "Training Data Area by Neighborhood")
plot(a2$Area, a2$Neighborhood, ylab = "BrkSide           Edwards           NAmes", main = "All Data Area By Neighborhood")

```


```