---
title: "p2 clean training data"
author: "Jonathan Tan"
date: "8/8/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

goal: sub in categorical variable "none" for missing NA's on certain variables
```{r data import}
train.data1 <- read.csv("D:/SMU/DS 6371 Stat Foundations For Data Science/PROJECT/train.csv")
test.data1 <- read.csv("D:/SMU/DS 6371 Stat Foundations For Data Science/PROJECT/test.csv")

```

```{r neighborhood scoped}
#narrow training data to relevant 3 neighborhoods

train.data2 <- train.data1[which(train.data1$Neighborhood == "NAmes" | train.data1$Neighborhood == "Edwards" | train.data1$Neighborhood == "BrkSide"), ]

test.data2 <- test.data1[which(train.data1$Neighborhood == "NAmes" | test.data1$Neighborhood == "Edwards" | test.data1$Neighborhood == "BrkSide"), ]
```

```{r print scoped test and train}
#setwd("D:/SMU/DS 6371 Stat Foundations For Data Science/PROJECT")
write.csv(train.data2, file = "training set 3 neighborhoods.csv")
write.csv(test.data2, file = "testing set 3 neighborhoods.csv")
```
look at table, values that can have NA logically replaced with "none" 
BsmtQual BsmtCond BsmtExposure BsmtFinType1 BsmtFinType2 Fireplace GarageType GarageFinish GarageQual GarageCond PoolQC Fence MscFeature Alley
GarageYrBlt currently looks like houses with no garages have 2000 year old garages, may throw off regerssion if we pick that variable 
```{r add "none"}
#first we'll try all replacing NA;s of certain columns with none? 
#test with garage type
summary(train.data2$GarageType)
change.locations <- c("BsmtQual", "BsmtCond", "BsmtExposure",  "BsmtFinType1", "BsmtFinType2", "Electrical",  "Fireplace", "GarageType", "GarageFinish", "GarageQual", "GarageCond", "PoolQC", "Fence", "MiscFeature ", "Alley")
q <- sapply(train.data2, is.factor) #check for factors whole dataframe
train.data2[q] <- lapply(train.data2[q], as.character) #change all factors to characters

train.data2[change.locations,][is.na(train.data2[change.locations,])] <- "None"
```
```{r specifics}
train.data2["LotFrontage"][is.na(train.data2["LotFrontage"])] <- "None"
train.data2["Alley"][is.na(train.data2["Alley"])] <- "None"
train.data2["BsmtQual"][is.na(train.data2["BsmtQual"])] <- "None"
train.data2["BsmtCond"][is.na(train.data2["BsmtCond"])] <- "None"
train.data2["BsmtExposure"][is.na(train.data2["BsmtExposure"])] <- "None"
train.data2["BsmtFinType1"][is.na(train.data2["BsmtFinType1"])] <- "None"
train.data2["BsmtFinType2"][is.na(train.data2["BsmtFinType2"])] <- "None"
train.data2["FireplaceQu"][is.na(train.data2["FireplaceQu"])] <- "None"
train.data2["GarageType"][is.na(train.data2["GarageType"])] <- "None"
train.data2["GarageYrBlt"][is.na(train.data2["GarageYrBlt"])] <- "None"
train.data2["GarageFinish"][is.na(train.data2["GarageFinish"])] <- "None"
train.data2["GarageQual"][is.na(train.data2["GarageQual"])] <- "None"
train.data2["GarageCond"][is.na(train.data2["GarageCond"])] <- "None"
train.data2["PoolQC"][is.na(train.data2["PoolQC"])] <- "None"
train.data2["Fence"][is.na(train.data2["Fence"])] <- "None"
train.data2["MiscFeature"][is.na(train.data2["MiscFeature"])] <- "None"
#might come back and get this to iterate through a list for the features, since the combined list doesn't seem to work

```

```{r print scoped test and train fith nones}
train.data3 <- train.data2
train.data4 <- as.factor(train.data3)
#test.data2 <- test.data3
#setwd("D:/SMU/DS 6371 Stat Foundations For Data Science/PROJECT")
write.csv(train.data3, file = "training set 3n as char.csv")
write.csv(train.data4, file = "training set 3n as factor.csv")
#write.csv(test.data2, file = "testing set 3 neighborhoods.csv")
```

```{r filter nas}
x <- colSums(is.na(train.data2)) #list of na's per column
y <- as.data.frame(x)
z <- subset(y, x != 0) #show only fields that have NA's in them 
names(z) <- c( "Number of NA's")
z
full <- subset(y, x == 0)#show columns with no na's
names(full) <- c("Variables with no NA's")
full
```

```{r replacement example }
set.seed(1234)
x <- data.frame(a=sample(c(1,2,NA), 10, replace=T),
                b=sample(c(1,2,NA), 10, replace=T), 
                c=sample(c(1:5,NA), 10, replace=T))

x[c("a", "b")][is.na(x[c("a", "b")])] <- "none"

y <- data.frame(train.data2$GarageType, train.data2$Fence, stringsAsFactors = FALSE)
z <- head(y, 20)
q <- sapply(z, is.factor) #checks if the column of the dataset is a factor 
#if it is -> 
z[q] <- lapply(z[q], as.character) #changes factor to character so we can use the next line under here 

z["train.data2.Fence"][is.na(z["train.data2.Fence"])] <- "None"
z
```